---
title: "sfPalette Usage"
author: "Anthony Caravaggi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sfPalette Colour Index}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

To display a colour swatch, simply call the `SF_palette` function and pass a palette name. Palette names can be found in the internal _mov_ dataframe. All colours are displayed by default.

```{r start}
library(sfPalettes)
data(mov)
mov
```

#### The Empire Strikes Back
```{r TESB, fig.height = 1}
SF_palette("TESB")
```

You can also specify the number of colours displayed by using the `n =` parameter.

#### Her
```{r Her, fig.height = 1}
SF_palette("HER", n = 4)
```

Palettes can be interopolated by extending `n =` beyond the number of available colours and using `type = continuous`.

#### Eternal Sunshine of the Spotless Mind
```{r ESSM, fig.height = 1}
SF_palette("ESSM", n = 24, type = "continuous")
```


You can also use SF_palettes to colour your plots, as below:

#### Scatterplot with the Jurassic Park palette
```{r JP}
library("ggplot2")
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  theme_bw() +
  geom_point(size = 3) +
  scale_color_manual(values = SF_palette("JP")) +
  labs(y = "Sepal width", x = "Sepal length") +
  theme(legend.text = element_text(face = "italic"))
```

#### Stacked barplot using The Martian
```{r TM}
qplot(factor(cyl), data = mtcars, geom = "bar", fill=factor(vs)) +
  scale_fill_manual(values = SF_palette("TM"))
```

#### A mountain created with Her
```{r HER2}
SF_colours_1 <- SF_palette("HER", 21, type = "continuous")
image(volcano, col = SF_colours_1, las = 1)
```

#### Heat map using Eternal Sunshine of the Spotless Mind
```{r ESSM2}
data(heatmap)  

SF_colours_2 <- SF_palette("ESSM", 100, type = "continuous")

ggplot(heatmap, aes(x = X2, y = X1, fill = value)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = SF_colours_2) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) + 
  coord_equal() 
```
